Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-12 talk/iwtc11/paper.tex
the example is from some other paper, cite that

For the purpose of this paper, we are going to use a tiny interpreter for a dynamic language with
 a very simple object
model, that just supports an integer and a float type. The objects support only
two operations, \lstinline{add}, which adds two objects (promoting ints to floats in a
mixed addition) and \lstinline{is_positive}, which returns whether the number is greater
than zero. The implementation of \lstinline{add} uses classical Smalltalk-like
double-dispatching.
%These classes could be part of the implementation of a very
%simple interpreter written in RPython.
The classes can be seen in
Figure~\ref{fig:objmodel} (written in RPython).

>>>>

For the purpose of this paper, we are going to use a tiny interpreter for a dynamic language with
 a very simple object
model, that just supports an integer and a float type (this example has been taken from a previous paper \cite{bolz_allocation_2011}). The objects support only
two operations, \lstinline{add}, which adds two objects (promoting ints to floats in a
mixed addition) and \lstinline{is_positive}, which returns whether the number is greater
than zero. The implementation of \lstinline{add} uses classical Smalltalk-like
double-dispatching.
%These classes could be part of the implementation of a very
%simple interpreter written in RPython.
The classes can be seen in
Figure~\ref{fig:objmodel} (written in RPython).
